D2F_exploration_fourway_and_GWAS

### 2020-06-05 R/D2F_exploration_fourway_and_gwas.Rmd
Manuscript changes completing draft of two environmental cues section

pid_all_sites <- phe %>%
  dplyr::select(PLANT_ID, ends_with("D2F")) %>%
  pivot_longer(cols = ends_with("D2F"), names_to = "SITE", values_to = "D2F") %>%
  group_by(PLANT_ID) %>%
  filter(!is.na(D2F) & !(SITE %in% c("FRMI_D2F", "BRKG_D2F", "TMPL_D2F"))) %>%
  count() %>% 
  arrange(desc(n)) %>%
  filter(n >= 4)
GR_start <- phe %>% 
  dplyr::select(-ends_with("D2F"), -ends_with("FL50")) %>%
  left_join(metadata, by = "PLANT_ID") %>%
  pivot_longer(cols = ends_with("GR50"), names_to = "SITE", values_to = "GR50") %>% 
  ungroup() %>%
  mutate(SITE = str_sub(SITE, end = 4)) %>%
  group_by(SITE, PLANT_ID) %>%
  summarise(GR_start = floor(min(GR50)))
FL_end <- phe %>% 
  dplyr::select(-ends_with("D2F"), -ends_with("GR50")) %>%
  left_join(metadata, by = "PLANT_ID") %>%
  pivot_longer(cols = ends_with("FL50"), names_to = "SITE", values_to = "FL50") %>%
  #filter(D2F > 10 & SUBPOP == "Midwest") %>%
  ungroup() %>%
  mutate(SITE = str_sub(SITE, end = 4)) %>%
  group_by(SITE, PLANT_ID) %>%
  summarise(FL_end = ceiling(max(FL50)))
tmp3 <- wea_df %>%
  left_join(GR_start, by = "SITE") %>%
  left_join(FL_end, by = c("SITE", "PLANT_ID")) %>%
  group_by(SITE, Day_of_year, PLANT_ID) %>%
  filter(between(Day_of_year, GR_start, FL_end)) %>% 
  ungroup()
```
CGDD plots
```{r}
tmp3 %>%
  group_by(SITE, PLANT_ID, GR_start, FL_end) %>%
  summarise(CGDD_13C = sum(GDD_13C_SM)
            ) %>%
  mutate(D2F = FL_end - GR_start) %>%
  filter(D2F > 10) %>%
  left_join(metadata) %>%
  left_join(sites) %>%
  filter(!(SITE %in% c("FRMI"))) %>%
  filter(PLANT_ID %in% pid_all_sites$PLANT_ID & SUBPOP %in% c("Midwest", "Gulf")) %>%
  ggplot(aes(x = Latitude, y = CGDD_13C)) + 
  geom_line(aes(group = PLANT_ID, color = SUBPOP)) + 
  #theme(legend.position = "none") +
  geom_text(aes(x = Latitude, label = SITE), y = 100, angle = 45) +
  geom_smooth(aes(group = SUBPOP), method = "lm")  +
  #geom_smooth(aes(group = SUBPOP), color = "green") +
  scale_color_viridis(discrete = TRUE, end = 0.8, direction = -1)  + 
  ylim(c(0,3200))

>>>>

pid_all_sites <- phe %>%
  dplyr::select(PLANT_ID, ends_with("D2F")) %>%
  pivot_longer(cols = ends_with("D2F"), names_to = "SITE", values_to = "D2F") %>%
  group_by(PLANT_ID) %>%
  filter(!is.na(D2F) & !(SITE %in% c("FRMI_D2F", "BRKG_D2F", "TMPL_D2F"))) %>%
  count() %>% a
  arrange(desc(n)) %>%
  filter(n >= 4)
GR_start <- phe %>% 
  dplyr::select(-ends_with("D2F"), -ends_with("FL50")) %>%
  left_join(metadata, by = "PLANT_ID") %>%
  pivot_longer(cols = ends_with("GR50"), names_to = "SITE", values_to = "GR50") %>% 
  ungroup() %>%
  mutate(SITE = str_sub(SITE, end = 4)) %>%
  group_by(SITE, PLANT_ID) %>%
  summarise(GR_start = floor(min(GR50)))
FL_end <- phe %>% 
  dplyr::select(-ends_with("D2F"), -ends_with("GR50")) %>%
  left_join(metadata, by = "PLANT_ID") %>%
  pivot_longer(cols = ends_with("FL50"), names_to = "SITE", values_to = "FL50") %>%
  #filter(D2F > 10 & SUBPOP == "Midwest") %>%
  ungroup() %>%
  mutate(SITE = str_sub(SITE, end = 4)) %>%
  group_by(SITE, PLANT_ID) %>%
  summarise(FL_end = ceiling(max(FL50)))
tmp3 <- wea_df %>%
  left_join(GR_start, by = "SITE") %>%
  left_join(FL_end, by = c("SITE", "PLANT_ID")) %>%
  group_by(SITE, Day_of_year, PLANT_ID) %>%
  filter(between(Day_of_year, GR_start, FL_end)) %>% 
  ungroup()
```
CGDD plots
```{r}
tmp3 %>%
  group_by(SITE, PLANT_ID, GR_start, FL_end) %>%
  summarise(CGDD_13C = sum(GDD_13C_SM)
            ) %>%
  mutate(D2F = FL_end - GR_start) %>%
  filter(D2F > 10) %>%
  left_join(metadata) %>%
  left_join(sites) %>%
  filter(!(SITE %in% c("FRMI"))) %>%
  filter(PLANT_ID %in% pid_all_sites$PLANT_ID & SUBPOP %in% c("Midwest", "Gulf")) %>%
  ggplot(aes(x = Latitude, y = CGDD_13C)) + 
  geom_line(aes(group = PLANT_ID, color = SUBPOP)) + 
  #theme(legend.position = "none") +
  geom_text(aes(x = Latitude, label = SITE), y = 100, angle = 45) +
  geom_smooth(aes(group = SUBPOP), method = "lm")  +
  #geom_smooth(aes(group = SUBPOP), color = "green") +
  scale_color_viridis(discrete = TRUE, end = 0.8, direction = -1)  + 
  ylim(c(0,3200))
